% Created 2020-07-03 Fri 13:57
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Md Suruz Miah}
\date{\textit{<2020-07-03 Fri>}}
\title{Emacs ORG-MODE}
\hypersetup{
 pdfauthor={Md Suruz Miah},
 pdftitle={Emacs ORG-MODE},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.0.91 (Org mode 9.3.7)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

\begin{quote}
This is a very messy document. This document is entirely done when I started thinking about writing notes using Emacs org-mode a long time ago. You may want to use some of the templates/styles mentioned here at your own risk! It absolutely comes with no warranty. 
\end{quote}



\section{Basic Usage of Org-mode}
\label{sec:orga73fd54}

This is under the section heading "Basic Usage of Org-mode"

\subsection{Itemize and Enumeration}
\label{sec:org4acb3ba}

This is under the subsection heading "Itemize and Enumeration"
\begin{itemize}
\item item 1
\item item 2
\item item 3

\textbf{bold} \emph{italic} \uline{underlined} \sout{strike-through} Greek letter \(\Gamma\)
\end{itemize}
Some enumerated  items 
\begin{enumerate}
\item First
\item Second
\item Third
\end{enumerate}

Inserting \href{http://www.personalpages.bradley.edu/\~smiah}{link} is very easy. Just type C-c C-l type the actual link followed by the description of the link that will appear in the document. 
\subsection{Quote and examples}
\label{sec:org16efc4e}

\begin{quote}
Everything should be made as simple as possible but not simpler -- Albert Einstein
\end{quote}

\begin{verbatim}
Here is an example
: Some example from a text file. 
\end{verbatim}


\subsection{Exporting Org Documents}
\label{sec:org0b4dc83}

I normally export org files to latex/pdf or html that includes latex math formulas/symbols and by default the exported files include title, author, date, \ldots{}  

\textbf{However, exporting Org file to Markdown does not include title, author, dates,\ldots{}} 

The default \emph{org-mode} does not have the option to export .org file to \emph{markdown} (.md file).   For that you will need to replace the \textbf{org} layer in \emph{dotspacemacs} file   with the   following 

\begin{verbatim}
(org :variables
     org-enable-github-support t)
\end{verbatim}


$$x = \sqrt{b}$$


\emph{Note: In case C-c C-e command doesn't show the export option for m (markdown), then simply open dotspacemacs file and compile it with M-SPC f e R. After that, you should see the option to export to markdown!} 
\end{document}